Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2020-08-10 FDT2020/main-section.tex
fixing typo
added comments in 2.1 and lemma 8

We introduce an algorithm that considers each of the variables iteratively, starting from the first coordinate and ending at the $t$-th coordinate. If the initial (integral) point $\tilde{x}$ has the variable set to $1$, the algorithm tries to reduce the variable to $0$ if possible. We run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and in each iteration we find $x^{(\ell)}\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$.
\cindy{I think the previous sentence also added to my confusion before (along with the term ``fix'' which I have replaced).  After $\ell$ iterations the first $\ell$ components are integer, but they were integer before.  Did you intend to say that we finalize a 0-1 value for the first $\ell$ coordinates?}
We can set $x^{(0)}=\tilde{x}$. Now consider the following linear program. The variables of this linear program are the $z\in \mathbb{R}^n$.
\begin{align}
\HelperLP(x^{(\ell)})\quad\quad& \min\quad \;z_{\ell+1}\\
&\;\text{s.t.} \quad \;\;Az\geq b \\
&\;{\color{white}{\text{s.t.}} }\quad \;\; \; z_j = x^{(\ell)}_j \quad \; j =1,\ldots, \ell\\
&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z_j \leq x^{(\ell)}_j \quad \; j = \ell+1,\ldots,n\\
&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z\;\geq 0
\end{align}

@@

	Let $x^0$, $x^1$, $\lambda_0$, and $\lambda_1$ be an optimal solution to the LP above. Set $\gamma_0=\lambda_0$ and $\gamma_1 = lambda_1$.
\cindy{The sentence right before this is how I think you link the $\lambda$ in the LP to the $\gamma$ constants in the Lemma statement and the claim below, etc.}
Let $\hat{x}^0 = x^0/\gamma_0$, $\hat{x}^1=x^1/\gamma_1$. This choice satisfies  (ii), (iii), (iv). To show that (i) is also satisfied we prove the following claim.

	\begin{claim}\label{CVexists}
		We have $\gamma_0 + \gamma_1\geq 1/g$.
	\end{claim}
	\begin{cproof}
		We show that there is a feasible solution that achieves the objective value of $\frac{1}{g}$. By Theorem \ref{CV2} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and $\tilde{x}^i\in S$ for $i\in[k]$ such that 
		$\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq gx'$. So

>>>>

We introduce an algorithm that considers each of the variables iteratively, starting from the first coordinate and ending at the $t$-th coordinate. If the initial (integral) point $\tilde{x}$ has the variable set to $1$, the algorithm tries to reduce the variable to $0$ if possible. \arash{A caution here: the phrase if possible a bit vague here. We round down to zero, if there is feasible solution to LP (so a point in $P(I)$, such that the first $\ell$ coordinates of it are all equal to the point $x^{(\ell)}$ that we have in iteration $\ell$ and its $\ell+1$-th coordinate is 0}. We run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and in each iteration we find $x^{(\ell)}\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$.
\cindy{I think the previous sentence also added to my confusion before (along with the term ``fix'' which I have replaced).  After $\ell$ iterations the first $\ell$ components are integer, but they were integer before.  Did you intend to say that we finalize a 0-1 value for the first $\ell$ coordinates?}
We can set $x^{(0)}=\tilde{x}$. Now consider the following linear program. The variables of this linear program are the $z\in \mathbb{R}^n$.
\begin{align}
\HelperLP(x^{(\ell)})\quad\quad& \min\quad \;z_{\ell+1}\\
&\;\text{s.t.} \quad \;\;Az\geq b \\
&\;{\color{white}{\text{s.t.}} }\quad \;\; \; z_j = x^{(\ell)}_j \quad \; j =1,\ldots, \ell\\
&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z_j \leq x^{(\ell)}_j \quad \; j = \ell+1,\ldots,n\\
&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z\;\geq 0
\end{align}

@@

	Let $x^0$, $x^1$, $\lambda_0$, and $\lambda_1$ be an optimal solution to the LP above. Set $\gamma_0=\lambda_0$ and $\gamma_1 = \lambda_1$.
\cindy{The sentence right before this is how I think you link the $\lambda$ in the LP to the $\gamma$ constants in the Lemma statement and the claim below, etc.}
Let $\hat{x}^0 = x^0/\gamma_0$, $\hat{x}^1=x^1/\gamma_1$. This choice satisfies  (ii), (iii), (iv). To show that (i) is also satisfied we prove the following claim.
	\arash{Now that I notice, we use $\lambda_0,\lambda_1,x^0,x^1}$ to represnt a feasible solution to the system 13-18. Since the optimal solution is use only for the duration of one sentence above maybe we can change the notation for the optimal solution. For instance use $y^0,y^1, \lambda^*_0,\lambda^*_1$}
	\begin{claim}\label{CVexists}
		We have $\gamma_0 + \gamma_1\geq 1/g$.
	\end{claim}
	\begin{cproof}
		We show that there is a feasible solution that achieves the objective value of $\frac{1}{g}$. By Theorem \ref{CV2} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and $\tilde{x}^i\in S$ for $i\in[k]$ such that 
		$\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq gx'$. So
